Selection of Polynomial Features by Genetic Algorithms

### 2013-09-05 texts/paper_spfga-final.tex
migrações

@@

\begin{figure*}[tb]\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
\begin{axis}[
	width=0.49\textwidth,height=4cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	yticklabels={0.7, 0.8, 0.9, 1.0, 1.1, 1.2, 1.3},
	title = {Dataset: \textsc{Abalone}},
	xlabel = {Error distribution},
	ylabel={Regularization weight ($\lambda$)},
	xmax=2.7,
	]	
	%\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/figure1.dat};
	\addplot[boxplot][fill=gray!50!white] table [y index=2] {data/figure1.dat};
	\addplot[boxplot] table [y index=4] {data/figure1.dat};
	\addplot[boxplot] table [y index=6] {data/figure1.dat};		
	\addplot[boxplot] table [y index=8] {data/figure1.dat};
	\addplot[boxplot] table [y index=10] {data/figure1.dat};
	\addplot[boxplot] table [y index=12] {data/figure1.dat};
\end{axis}	
\end{tikzpicture}
%
% RIGHT PANE
&
%
%
\begin{tikzpicture}
\begin{axis}[
	width=0.49\textwidth,height=4cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	%yticklabels={0.7, 0.8, 0.9, 1.0, 1.1, 1.2, 1.3},
	yticklabels={},
	title = {Dataset: \textsc{Auto MPG}},
	xlabel = {Error distribution},
	ylabel={},
	]	
	%\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot][fill=gray!50!white] table [y index=2] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=4] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=6] {data/lambda.errors.Auto-Mpg.dat};		
	\addplot[boxplot] table [y index=8] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=10] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=12] {data/lambda.errors.Auto-Mpg.dat};

\end{axis}
\end{tikzpicture}
\end{tabular}

@@

\begin{figure}[tb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=0.48\textwidth,height=4cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6},
	%yticklabels={GA.Poly,Rnd.For,Lin.Reg,SVM,RPART,CI.Tree},
	ylabel={Method index},
	xmin=-25,
	xmax=325,
	xlabel={Error distribution},
	title={Dataset: \textsc{Artificial}},
	]
	%\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot][fill=gray!50!white] table [y index=0] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=4] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=1] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=2] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=3] {data/Articial_dataset.dat};
	\addplot[boxplot] table [y index=5] {data/Articial_dataset.dat};

@@

\newcommand{\axpl}[3]{
\begin{axis}[width=0.49\textwidth,height=4cm,
	ticks=major,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6},
	%yticklabels={GA.Poly, Lin.Reg, SVM, RPART,Rnd.For,CI.Tree},
	title={Dataset: \textsc{#2}},
	ylabel={Method index},
	xlabel={Error distribution},
	separate axis lines,
	axis lines = box,
%	axis y line = #3,
	]
	%\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot][fill=gray!50!white] table [y index=0] {data/#1.dat};
	\addplot[boxplot] table [y index=4] {data/#1.dat};
	\addplot[boxplot] table [y index=1] {data/#1.dat};
	\addplot[boxplot] table [y index=2] {data/#1.dat};
	\addplot[boxplot] table [y index=3] {data/#1.dat};
	\addplot[boxplot] table [y index=5] {data/#1.dat};

\end{axis}
}

\begin{figure*}[tb]\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
	\axpl{Housing300_lambda0.8_25runs}{Housing}{left}
\end{tikzpicture}
%
&
%
\begin{tikzpicture}
	\axpl{Abalone300_lambda0.8_25runs}{Abalone}{right}
\end{tikzpicture}
%
\\
%
\begin{tikzpicture}
	\axpl{Auto-Mpg300_lambda0.8_25runs}{Auto MPG}{left}
\end{tikzpicture}
%
&
%
\begin{tikzpicture}
	\axpl{Kinematics300_lambda0.8_25runs}{Kinematics}{right}
\end{tikzpicture}

\end{tabular}

\caption{Summary results for different regression methods on the Housing, Abalone, Auto MPG and Kinematics datasets. Random Forests, an ensemble method (``2'' in the plots), has the better results. However \ac{GAPoly} achieves similar errors in two of the datasets. For the remaining two \ac{GAPoly} produces similar errors to the other classic regression methods.  The regression methods depicted in these figures are: 1. \ac{GAPoly}, 2. Random Forests, 3. Linear Regression, 4. SVM, 5. Regression Trees and 6. Conditional Inference Trees}
\label{Housing_dataset_lambda0.8_25runs}
\label{Abalone_dataset_lambda0.8_25runs}
\label{Auto-Mpg_dataset_lambda0.8_25runs}
\label{Kinematics300_lambda0.8_25runs}
\end{center}\end{figure*}

@@

	\addplot[solid,color=black] table [x expr=\coordindex, y index = 0] {data/lambdas.dat};\addlegendentry{$\lambda=0.975$};
	\addplot[dashed,color=black] table [x expr=\coordindex, y index = 1] {data/lambdas.dat};\addlegendentry{$\lambda=1.000$};
\end{axis}
\end{tikzpicture}
\caption{Error progress for Abalone dataset during a single execution of the genetic algorithm. The figure shows the fitness evolution for two different regularization values. The population for both consisted of $200$ polynomials. The error values seem to stabilize around iteration~250.}
\label{Abalone_fitnessProgress}

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%	EMBEDDED DATASETS
%
\begin{filecontents}{inlambdas.dat}
2.474 2.460
2.414 2.392
2.414 2.392
2.414 2.392
2.407 2.392
2.407 2.392
2.317 2.331
2.351 2.331
2.330 2.331
2.314 2.318
2.251 2.318
2.251 2.318
2.251 2.318
2.275 2.318
2.275 2.318
2.275 2.318
2.275 2.318
2.275 2.296
2.275 2.296
2.268 2.296
2.268 2.296
2.268 2.296
2.225 2.296
2.225 2.296
2.225 2.296
2.225 2.296
2.225 2.296
2.225 2.296
2.225 2.268
2.225 2.268
2.225 2.268
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.261
2.225 2.247
2.225 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.247
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.200 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.238
2.185 2.221
2.185 2.221
\end{filecontents}

@@

%
\newcommand{\boxp}[6]{\addplot
	[boxplot prepared={
		lower whisker=#1,
		lower quartile=#2,
		median=#3,
		upper quartile=#4,
		upper whisker=#5,
	},][fill=#6!50!white] coordinates {}}
%
\begin{figure*}[tb]\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
\begin{axis}[
	width=0.49\textwidth,height=4cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	yticklabels={0.7, 0.8, 0.9, 1.0, 1.1, 1.2, 1.3},
	title = {Dataset: \textsc{Abalone}},
	xlabel = {Error distribution},
	ylabel={Regularization weight ($\lambda$)},
	]	
	%
	%	Original dataset: data/figure1.dat
	%	y indexes: 0,2,4,6,8,10,12
	%
	\boxp{2.18}{2.21}{2.27}{2.33}{2.36}{white};	
	\boxp{2.12}{2.15}{2.16}{2.23}{2.34}{gray};						
	\boxp{2.18}{2.20}{2.23}{2.29}{2.33}{white};
	\boxp{2.15}{2.16}{2.20}{2.29}{2.31}{white};
	\boxp{2.46}{2.465}{2.47}{2.473}{2.476}{white};
	\boxp{2.44}{2.48}{2.62}{2.65}{2.655}{white};
	\boxp{2.36}{2.47}{2.55}{2.56}{2.61}{white};	
\end{axis}	
\end{tikzpicture}
%
% RIGHT PANE
&
%
%
\begin{tikzpicture}
\begin{axis}[
	width=0.49\textwidth,height=4cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6,7},
	yticklabels={},
	title = {Dataset: \textsc{Auto MPG}},
	xlabel = {Error distribution},
	ylabel={},
	]
	%
	%	Original dataset: data/lambda.errors.Auto-Mpg.dat
	%	y indexes: 0,2,4,6,8,10,12
	%
	\boxp{2.27}{2.63}{2.79}{2.87}{3.09}{white};
	\boxp{2.41}{2.55}{2.65}{2.757}{2.88}{gray};	
	\boxp{2.45}{2.58}{2.76}{2.88}{3.02}{white};	
	\boxp{2.73}{2.731}{2.82}{2.86}{2.87}{white};	
	\boxp{2.69}{2.86}{3.04}{3.27}{3.53}{white};
	\boxp{2.68}{3.12}{3.37}{3.67}{3.86}{white};
	\boxp{3.84}{4.22}{4.33}{4.5}{4.8}{white};
\end{axis}
\end{tikzpicture}
\end{tabular}

@@

\begin{figure}[tb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=0.48\textwidth,height=4cm,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6},
	ylabel={Method index},
	xmin=-25,
	xmax=350,
	xlabel={Error distribution},
	title={Dataset: \textsc{Artificial}},
	]
	%
	%	Original dataset: data/Articial_dataset.dat
	%	y indexes: 0,4,1,2,3,5
	%	cols #3 and #5 have the same values
	%
	\boxp{-0.005}{-0.001}{0.0}{0.001}{0.005}{gray};	
	\boxp{152.18}{195.59}{213.88}{246.72}{314.78}{white};	
	\boxp{63.69}{82.96}{87.07}{103.68}{134.66}{white};	
	\boxp{56.10}{81.39}{87.70}{114.82}{157.83}{white};		
	\boxp{137.46}{166.65}{196.00}{225.99}{284.15}{white};
	\boxp{137.46}{166.65}{196.00}{225.99}{284.15}{white};

@@

\newcommand{\axpla}[3]{
\begin{axis}[width=0.49\textwidth,height=4cm,
	ticks=major,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6},
	%yticklabels={GA.Poly, Lin.Reg, SVM, RPART,Rnd.For,CI.Tree},
	title={Dataset: \textsc{#2}},
	ylabel={Method index},
	xlabel={Error distribution},
	separate axis lines,
	axis lines = box,
%	axis y line = #3,
	]
	%\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot][fill=gray!50!white] table [y index=0] {data/#1.dat};
	\addplot[boxplot] table [y index=4] {data/#1.dat};
	\addplot[boxplot] table [y index=1] {data/#1.dat};
	\addplot[boxplot] table [y index=2] {data/#1.dat};
	\addplot[boxplot] table [y index=3] {data/#1.dat};
	\addplot[boxplot] table [y index=5] {data/#1.dat};

\end{axis}
}
\newcommand{\axpl}[2]{
\begin{axis}[width=0.49\textwidth,height=4cm,
	ticks=major,
	boxplot/draw direction=x,
	ytick={1,2,3,4,5,6},
	title={Dataset: \textsc{#1}},
	ylabel={Method index},
	xlabel={Error distribution},
	separate axis lines,
	axis lines = box,
	]
#2
\end{axis}
}

\begin{figure*}[tb]\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
	\axpl{Housing}{
	\boxp{0.39}{0.50}{0.54}{0.64}{0.85}{gray};
	\boxp{0.29}{0.34}{0.37}{0.40}{0.48}{white};
	\boxp{0.46}{0.51}{0.55}{0.56}{0.61}{white};
	\boxp{0.46}{0.53}{0.57}{0.60}{0.67}{white};
	\boxp{0.40}{0.48}{0.54}{0.57}{0.66}{white};
	\boxp{0.41}{0.46}{0.51}{0.55}{0.62}{white};
	}
\end{tikzpicture}
%
&
%
\begin{tikzpicture}
	\axpl{Abalone}{
	\boxp{0.6497}{0.6743}{0.685}{0.6948}{0.7213}{gray};
	\boxp{0.6494}{0.6684}{0.6745}{0.6812}{0.698}{white};
	\boxp{0.6797}{0.6874}{0.6937}{0.6966}{0.7092}{white};
	\boxp{0.6736}{0.6959}{0.7043}{0.7111}{0.7249}{white};
	\boxp{0.7201}{0.7459}{0.7551}{0.7638}{0.7876}{white};
	\boxp{0.6829}{0.7038}{0.7179}{0.7274}{0.7587}{white};
	}
\end{tikzpicture}
%
\\
%
\begin{tikzpicture}
	\axpl{Auto MPG}{
	\boxp{0.3234}{0.3423}{0.3744}{0.3919}{0.4264}{gray};
	\boxp{0.3056}{0.3311}{0.3607}{0.3731}{0.4169}{white};
	\boxp{0.371}{0.4042}{0.4153}{0.4341}{0.4763}{white};
	\boxp{0.3696}{0.4122}{0.4286}{0.4476}{0.491}{white};
	\boxp{0.3887}{0.4234}{0.445}{0.479}{0.5106}{white};
	\boxp{0.3636}{0.3927}{0.4245}{0.4635}{0.4969}{white};
	}
\end{tikzpicture}%
&
%
\begin{tikzpicture}
	\axpl{Kinematics}{
	\boxp{0.7434}{0.759}{0.7641}{0.7804}{0.7947}{gray};
	\boxp{0.564}{0.5686}{0.5717}{0.5771}{0.587}{white};
	\boxp{0.7473}{0.7625}{0.7676}{0.776}{0.7821}{white};
	\boxp{0.7535}{0.7697}{0.7781}{0.7827}{0.792}{white};
	\boxp{0.7974}{0.8097}{0.8211}{0.8292}{0.8377}{white};
	\boxp{0.7328}{0.744}{0.7555}{0.7633}{0.778}{white};
	}
\end{tikzpicture}
%
\end{tabular}

%
%	Generate "boxplot prepared" parameters
%
%\begin{tikzpicture}
%\newcommand{\dataset}{Kinematics300_lambda0.8_25runs}
%\newcommand{\colindex}{5} % 0 4 1 2 3 5
%\begin{axis}[
%	boxplot/draw direction=x,
%	ymax=2,
%	%xmin=0.79,xmax=0.85,
%	]
%	\addplot[boxplot][fill=green!50!white] table [y index=\colindex] {data/\dataset.dat} [above]
%	node at (boxplot box cs: \boxplotvalue{median},1)
%  		{\{\pgfmathprintnumber[precision=4]{\boxplotvalue{lower whisker}}\}\{\pgfmathprintnumber[precision=4]{\boxplotvalue{lower quartile}}\}\{\pgfmathprintnumber[precision=4]{\boxplotvalue{median}}\}\{\pgfmathprintnumber[precision=4]{\boxplotvalue{upper quartile}}\}\{\pgfmathprintnumber[precision=4]{\boxplotvalue{upper whisker}}\}};
%
%\end{axis}
%
%\end{tikzpicture}
\caption{Summary results for different regression methods on the Housing, Abalone, Auto MPG and Kinematics datasets. Random Forests, an ensemble method (``2'' in the plots), has the better results. However \ac{GAPoly} achieves similar errors in two of the datasets. For the remaining two \ac{GAPoly} produces similar errors to the other classic regression methods.  The regression methods depicted in these figures are: 1. \ac{GAPoly}, 2. Random Forests, 3. Linear Regression, 4. SVM, 5. Regression Trees and 6. Conditional Inference Trees}
\label{Housing_dataset_lambda0.8_25runs}
\label{Abalone_dataset_lambda0.8_25runs}
\label{Auto-Mpg_dataset_lambda0.8_25runs}
\label{Kinematics300_lambda0.8_25runs}
\end{center}\end{figure*}

@@

	\addplot[solid,color=black] table [x expr=\coordindex, y index = 0] {inlambdas.dat};\addlegendentry{$\lambda=0.975$};
	\addplot[dashed,color=black] table [x expr=\coordindex, y index = 1] {inlambdas.dat};\addlegendentry{$\lambda=1.000$};
\end{axis}
\end{tikzpicture}
\caption{Error progress for Abalone dataset during a single execution of the genetic algorithm. The figure shows the fitness evolution for two different regularization values. The population for both consisted of $200$ polynomials. The error values seem to stabilize around iteration~250.}
\label{Abalone_fitnessProgress}
